\textit{Supplementary materials for: } High-level cognition during story listening is reflected in high-order dynamic correlations in neural activity patterns

### 2021-07-12 paper/supplementary_materials.tex
updates to figure legends

\begin{figure}[p!]
\centering
\includegraphics[width=0.95\textwidth]{figs/sim_heatmaps_features}
  \caption{\textbf{Recovery heatmap of simulated first-order and
      second-order dynamic correlations across features and widths.}  Each panel displays a
    heatmap of the average correlations
    between the vectorized upper triangles of the recovered
    first-order and second-order correlation matrices and the true
    (simulated) first-order and second order correlation matrices.
    The averages are taken across several randomly generated
    synthetic datasets for each timeseries pattern (constant, random,
    ramping, and data; see Synthetic data: simulating dynamic higher-order
      correlations).  The $x$-axes of each heatmap denote varying
    Laplace-shaped kernel widths (see Figs.~\ref{fig:supp_kernels}
    and~\ref{fig:supp_widths}), and the $y$-axes of each heatmap
    denote varying numbers of features ($K$) used in each of the synthetic datasets.
    A total of 10 synthetic datasets were generated for each number of features
    (row) and timeseries pattern (panel).}
\label{fig:features}
\end{figure}

\begin{figure}[p!]
\centering
\includegraphics[width=0.75\textwidth]{figs/supp_15_intact}
\caption{\textbf{Top terms associated with the most strongly
      correlated nodes at each order, for the intact experimental
    condition.}  Each color corresponds to one order of inter-subject
functional correlations. The inflated brain plots display the
locations of the endpoints of the 10 strongest (absolute value)
correlations at each order, projected onto the cortical
surface~\citep{CombEtal19}.  The lists of terms display
the top 10 Neurosynth terms~\citep{RubiEtal17} decoded from the
corresponding brain maps for each order.  (Also see Fig.~\neurosynth,
top row, in the main text.)}
\label{fig:intact}
\end{figure}

\begin{figure}[p!]
\centering
\includegraphics[width=0.75\textwidth]{figs/supp_15_paragraph}
\caption{\textbf{Top terms associated with the most strongly
      correlated nodes at each order, for the paragraph experimental
    condition.}  This figure is in the same format as
  Figure~\ref{fig:intact}, but displays results for the
  paragraph-scrambled story listening condition.  (Also see Fig.~\neurosynth,
second row, in the main text.)}
\label{fig:paragraph}
\end{figure}

\begin{figure}[p!]
\centering
\includegraphics[width=0.75\textwidth]{figs/supp_15_word}
\caption{\textbf{Top terms associated with the most strongly
      correlated nodes at each order, for the word experimental
    condition.}  This figure is in the same format as
  Figure~\ref{fig:intact}, but displays results for the
  word-scrambled story listening condition.  (Also see Fig.~\neurosynth,
third row, in the main text.)}
\label{fig:word}
\end{figure}

\begin{figure}[p!]
\centering
\includegraphics[width=0.75\textwidth]{figs/supp_15_rest}
\caption{\textbf{Top terms associated with the most strongly
      correlated nodes at each order, for the rest experimental
    condition.}  This figure is in the same format as
  Figure~\ref{fig:intact}, but displays results for the
  resting state condition.  (Also see Fig.~\neurosynth,
bottom row, in the main text.)}
\label{fig:rest}
\end{figure}

\begin{figure}[p!]
\centering
\includegraphics[width=0.75\textwidth]{figs/pca}
\caption{\textbf{Cumulative percent variance explained as a function
    of the number of principle components.}  Order refers to the order of the dynamic
    correlations calculated. Principle components analysis was
    performed, and reduced independently for each subject.  Maximum number of components varies with
    the total time for each condition (intact: 300; paragraph: 272;
    word: 300; rest: 400). \textbf{a.~Cumulative percent
    variance as a function of number of components for Order 0.} PCA
  was performed on the raw activity patterns (Order 0). \textbf{b.-e.~Cumlative percent
    variance as a function of number of components for Orders 1.-4.:
    PCA} Dynamic correlation were calculated for orders 1-4 using PCA to
    project each high-dimensional pattern of dynamic correlations onto
    a lower-dimensional space.   \textbf{f.-i.~Cumlative percent
    variance as a function of number of components for Orders 1.-4.: eigenvector centrality.} These panels are in the
    same format as Panel b.-e., but here eigenvector centrality has been
    used to project the high-dimensional patterns of dynamic
    correlations onto a lower-dimensional space. }
\label{fig:pca}
\end{figure}

>>>>

\begin{figure}[p!]
\centering
\includegraphics[width=0.95\textwidth]{figs/sim_heatmaps_features}
  \caption{\textbf{Recovery heatmap of simulated first-order and
      second-order dynamic correlations across features and widths.}  Each panel displays a
    heatmap of the average correlations
    between the vectorized upper triangles of the recovered
    first-order and second-order correlation matrices and the true
    (simulated) first-order and second order correlation matrices.
    The averages are taken across several randomly generated
    synthetic datasets for each timeseries pattern (constant, random,
    ramping, and data; see Synthetic data: simulating dynamic higher-order
      correlations).  The $x$-axes of each heatmap denote varying
    Laplace-shaped kernel widths (see Figs.~\ref{fig:supp_kernels}
    and~\ref{fig:supp_widths}), and the $y$-axes of each heatmap
    denote varying numbers of features ($K$) used in each of the synthetic datasets.
    A total of 10 synthetic datasets were generated for each number of features
    (row) and timeseries pattern (panel). Source data are provided as a Source Data file.}
\label{fig:features}
\end{figure}

\begin{figure}[p!]
\centering
\includegraphics[width=0.75\textwidth]{figs/supp_15_intact}
\caption{\textbf{Top terms associated with the most strongly
      correlated nodes at each order, for the intact experimental
    condition.}  Each color corresponds to one order of inter-subject
functional correlations. The inflated brain plots display the
locations of the endpoints of the 10 strongest (absolute value)
correlations at each order, projected onto the cortical
surface~\citep{CombEtal19}.  The lists of terms display
the top 10 Neurosynth terms~\citep{RubiEtal17} decoded from the
corresponding brain maps for each order.  (Also see Fig.~\neurosynth,
top row, in the main text.) Source data are provided as a Source Data file.}
\label{fig:intact}
\end{figure}

\begin{figure}[p!]
\centering
\includegraphics[width=0.75\textwidth]{figs/supp_15_paragraph}
\caption{\textbf{Top terms associated with the most strongly
      correlated nodes at each order, for the paragraph experimental
    condition.}  This figure is in the same format as
  Figure~\ref{fig:intact}, but displays results for the
  paragraph-scrambled story listening condition.  (Also see Fig.~\neurosynth,
second row, in the main text.) Source data are provided as a Source Data file.}
\label{fig:paragraph}
\end{figure}

\begin{figure}[p!]
\centering
\includegraphics[width=0.75\textwidth]{figs/supp_15_word}
\caption{\textbf{Top terms associated with the most strongly
      correlated nodes at each order, for the word experimental
    condition.}  This figure is in the same format as
  Figure~\ref{fig:intact}, but displays results for the
  word-scrambled story listening condition.  (Also see Fig.~\neurosynth,
third row, in the main text.) Source data are provided as a Source Data file.}
\label{fig:word}
\end{figure}

\begin{figure}[p!]
\centering
\includegraphics[width=0.75\textwidth]{figs/supp_15_rest}
\caption{\textbf{Top terms associated with the most strongly
      correlated nodes at each order, for the rest experimental
    condition.}  This figure is in the same format as
  Figure~\ref{fig:intact}, but displays results for the
  resting state condition.  (Also see Fig.~\neurosynth,
bottom row, in the main text.) Source data are provided as a Source Data file.}
\label{fig:rest}
\end{figure}

\begin{figure}[p!]
\centering
\includegraphics[width=0.75\textwidth]{figs/pca}
\caption{\textbf{Cumulative percent variance explained as a function
    of the number of principle components.}  Order refers to the order of the dynamic
    correlations calculated. Principle components analysis was
    performed, and reduced independently for each subject.  Maximum number of components varies with
    the total time for each condition (intact: 300; paragraph: 272;
    word: 300; rest: 400). \textbf{a.~Cumulative percent
    variance as a function of number of components for Order 0.} PCA
  was performed on the raw activity patterns (Order 0). \textbf{b.-e.~Cumlative percent
    variance as a function of number of components for Orders 1.-4.:
    PCA} Dynamic correlation were calculated for orders 1-4 using PCA to
    project each high-dimensional pattern of dynamic correlations onto
    a lower-dimensional space.   \textbf{f.-i.~Cumlative percent
    variance as a function of number of components for Orders 1.-4.: eigenvector centrality.} These panels are in the
    same format as Panel b.-e., but here eigenvector centrality has been
    used to project the high-dimensional patterns of dynamic
    correlations onto a lower-dimensional space. Source data are provided as a Source Data file.}
\label{fig:pca}
\end{figure}
